---
title: "index.Rmd"
author: "Dine Mamadou"
output: 
  html_document:
    highlight: kate
    keep_md: yes
    theme: united
---
#General Observations
The languageR data sets are pretty messy and the hardest thing about them was the length of long data. That is the reaon why I used `slice()' to reduce it to the most essential parts. Also, not all variables correlate, so it required several trials to get to find the few that do. Finally, instead of a regression line as asked in the directions for this homework, I provided a line of best fit. It's certainly the case that these two lines don't exactly do the same think. If this is true, what is the difference between them?

```{r setup, include=FALSE}
library(tidyverse)
library(languageR)
#this shouldn't show.
library(tidyverse)
library(languageR)
```

#Tiding the data

###Using 'gather( )'

``` {r}
beginningReaders %>%
  select(PC1, PC2, PC3, PC4) %>%
  gather(., key = PC, val = Measurements) %>%
  ggplot(., aes(x = PC, y = Measurements), color = PC) +
    geom_boxplot()

```


###Using 'separate( )'

```{r}
beginningReaders %>%
  select(., PC2) %>%
  slice(., 1:20) %>%
  separate(., PC2, into = c('Subcondition', 'Subcondition')) 
```
#Some descriptive data & fitting a model
```{r}
model <- lm(formula = PC1 ~ PC3, data = beginningReaders)
  summary(model)
  coefficients(model)

```
#Fitting a regression line to the data 
```{r}

beginningReaders %>%
  select(., PC1, PC3) %>%
  ggplot(., aes(x = PC1, y = PC3)) +
  geom_point() +
   geom_smooth()
```

#Final boxplot

```{r}
beginningReaders %>%
  select(., Word, PC1) %>%
  slice(., 1:200) %>%
  ggplot(., aes(x = Word, y = PC1, color = Word)) +
  geom_boxplot()
```
